Concurrent Programming in Harmony

### 2021-07-24 book/paper.tex
Latest

Leader election is the problem of electing a unique leader in a network
of processors.  Typically the processors have only limited information.
In the version that we present, each processor has a unique identifier.  The
processors are organized in a ring, but each processor only knows its
own identifier and the identifier of its successor.  We assume that
each processor can reliably send messages to its successor.

@@

Distributed consensus is the problem of having a collection of processors agree
on a single value over a network.  This often has to be done in adverse circumstances,
for example in the face of processor failures.
In Harmony, processors can be modeled by threads and there are a variety of ways in
which one can model a network using shared variables.
In this chapter, we will present a simple consensus algorithm that can tolerate
fewer than $1/3^{rd}$ of processors failing by crashing.

>>>>

Leader election is the problem of electing a unique leader in a network
of processors.  Typically the processors have only limited information.
In the version that we present, each processor has a unique identifier.  The
processors are organized in a ring, but each processor only knows its
own identifier and the identifier of its successor.  Having already
looked into the problem of how to make the network reliable,
we assume here that each processor can reliably send messages to its
successor.

@@

Distributed consensus is the problem of having a collection of processors agree
on a single value over a network.
Without failures, this can be solved using leader election: first elect a leader, then have that leader decide a value.
But consensus often has to be done in adverse circumstances,
for example in the face of processor failures.
In Harmony, processors can be modeled by threads and there are a variety of ways in
which one can model a network using shared variables.
In this chapter, we will present a simple consensus algorithm that can tolerate
fewer than $1/3^{rd}$ of processors failing by crashing.
